---
title: "Assignment03"
author: "zerofrom"
date: "`r Sys.Date()`"
output:
  pdf_document: null
  latex_engine: xelatex
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(Stat2Data)
library(dplyr)
```
# 1. Data Wrangling
```{r}
data("Hawks")
```

## 1 (Q1) 
```{r}
hawksSmall<-
drop_na(select(Hawks,Age,Day,Month,Year,CaptureTime,Species,Wing,Weight,Tail))
number<- dim(hawksSmall)
print(number)
head(hawksSmall,5)
```

## 1 (Q2) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Weight) 
) +
  geom_histogram(
    binwidth = 10
  ) +
  labs(
    x="Weight",
    y="Count"
   ) +
  theme_minimal()

```

## 1 (Q3) 
```{r}
# adjust = 0.5 
p1 <- ggplot(hawksSmall, aes(x=Tail)) +
  geom_density(adjust=0.5) +
  labs(
    x="Tail length",
    y="Count"
  )

# adjust = 2
p2 <- ggplot(hawksSmall, aes(x=Tail)) +
  geom_density(adjust=2) +
  labs(
    x="Tail length",
    y="Count"
  )
p1
p2
```

## 1 (Q4) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,color=Species)
  )+
  geom_density(
    adjust=1
    ) +
  labs(
    x="Tail length",
    y="Count"
  )
```

## 1 (Q5) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,y=Species,fill=Species)
)+
  geom_violin()+
  labs(
    x="Tail(mm)",
    y="Density"
  )
```

## 1 (Q6) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,y=Weight,color=Species,shape=Species)
)+
  geom_point()+
  labs(
    x="Tail(mm)",
    y="Weight(mm)"
  )
```  

1. There are 4 aesthetics: x=Tail,y=Weight,color=Species,shape=Species.  
2. Points.  
3. Color: Different colors refers to different species.  
   Shape: Different shapes refers to different species.  
   Axes Labels: These provide context for what the x(Tail length) and y(Weight) axes represent.  
   
## 1 (Q7)
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,y=Weight,color=Species)
)+
  geom_point()+
  geom_smooth(method = "lm")+
  facet_wrap(~Species,scales="free")+
  labs(
    x="Tail(mm)",
    y="Weight(mm)"
  )
```  

1. Color: Used to differentiate between species.  
   Line: A trend line indicates the relationship between Tail and Weight.  
3.The trend line shows a positive slope, which suggests positive correlation between the weight of the hawks and their tail lengths. 

## 1 (Q8)
```{r}
heaviest_hawk <-hawksSmall %>%
  filter(Weight == max(Weight)) %>%
  select(Tail, Weight)

ggplot(
  hawksSmall,
  aes(x=Tail,y=Weight,color=Species,shape=Species)
)+
  geom_point()+
  labs(
    x="Tail(mm)",
    y="Weight(mm)"
  )+
  geom_curve(
    aes(x=heaviest_hawk$Tail, y=heaviest_hawk$Weight-200,
        xend=heaviest_hawk$Tail, yend=heaviest_hawk$Weight),
    curvature = 0.5,
    arrow = arrow(length=unit(0.01,"inches"),
                  type="closed"),
    color="black"
  )+
  geom_point(
    aes(x=heaviest_hawk$Tail, y=heaviest_hawk$Weight),
    shape=16,
    size=1,
    color="black"
  )+
  annotate("text",
           x=heaviest_hawk$Tail,
           y=heaviest_hawk$Weight -200,
           label="heaviest hawk")
```

# 2. Finite probability spaces
- \(n = 10\)    : number of balls.
- \(r = 3\)     : number of red balls.
- \(n - r = 7\) : number of blue balls.
- \(k = 22\)    : repeat times.
- \(q = z\)     : red balls in repeat times.
$$
P(X = z) = \binom{k}{q} \left( \frac{r}{n} \right)^z \left(\frac{n-r}{n} \right)^{k - z} \label{eq:finite_space}
$$
## 2 (Q1)  
#### the probability that z out of the 22 selections were red spheres
$$
P(X = z) = \binom{22}{z} \left( \frac{3}{10} \right)^z \left(\frac{7}{10} \right)^{22 - z} \label{eq:example_calculation}
$$

## 2 (Q2)
```{r}
prob_red_spheres <- function(z){
  n <- 10
  r <- 3
  k <- 22
  prob <- choose(k,z) * (r/n)^z * ((n-r)/n)^(k-z)
  return(prob)
}
print(prob_red_spheres(10))
```

## 2 (Q3)
```{r}
num_reds <- seq(1:22)
prob <- sapply(num_reds, prob_red_spheres)
prob_by_num_reds = data.frame(num_reds = num_reds, prob = prob)
prob_by_num_reds %>% head(3)
```

## 2 (Q4)
```{r}
ggplot(
  prob_by_num_reds,
  aes(x=num_reds,y=prob)
)+
  geom_line()+
  labs(x="Number of reds", y="Probability")
```

## 2 (Q5)
### 2 (Q5.1)
```{r}
## case 1: Setting the random seed just once
set.seed(0)
for(i in 1:5){
 print(sample(100,5,replace=FALSE))
 # The result may well differ every time
}
## case 2: Resetting the random seed every time
set.seed(1)
print(sample(100,5,replace=FALSE))
set.seed(1)
print(sample(100,5,replace=FALSE))
set.seed(1)
print(sample(100,5,replace=FALSE))
# The result should not change
## case 3: reproducing case 1 if we set a random seed at the beginning. 
set.seed(0)
for(i in 1:5){
 print(sample(100,5,replace=FALSE))
} # The result will be 5 samples exactly the same as in case 1 (why?).
```
### 2 (Q5.2)
```{r}
itermap <- function(.x, .f) {
 result <- list()
 for (item in .x) {
 result <- c(result, list(.f(item)))
 }
 return(result)
}
itermap( c(1,2,3), function(x){ return(c(x,x^2)) } )

itermap_dbl <- function(.x, .f) {
 result <- numeric(length(.x))
 for (i in 1:length(.x)) {
 result[i] <- .f(.x[[i]])
 }
 return(result)
}
itermap_dbl( c(1,2,3), function(x){ return(x^3) } )
```
### 2 (Q5.3)
```{r}
num_trials <- 1000
set.seed(0)
sampling_with_replacement_simulation<-data.frame(trial=1:num_trials) %>%
  mutate(sample_balls = itermap(.x=trial, function(x){sample(10,22, replace = TRUE)})) %>%
  mutate(num_reds = itermap_dbl(sample_balls, 
                                function(x){
                                  sum(x<=3)
                                }))
head(sampling_with_replacement_simulation, 3)
```

## 2 (Q6)
```{r}
num_reds_in_simulation <- sampling_with_replacement_simulation %>% 
  pull(num_reds)
prob_by_num_reds <- prob_by_num_reds %>%
  mutate(predicted_prob = itermap_dbl(num_reds,
                                      function(.x){
                                        sum(num_reds_in_simulation == .x)/num_trials
                                      }))
head(prob_by_num_reds, 5)
```

## 2 (Q7)
```{r}
prob_by_num_reds %>%
 rename(TheoreticalProbability=prob, 
EstimatedProbability=predicted_prob) %>%
 ggplot() + geom_line(aes(x=num_reds, y=TheoreticalProbability)) +
 geom_line(aes(x=num_reds, y=EstimatedProbability), linetype='dashed') +
 geom_point(aes(x=num_reds, y=EstimatedProbability)) + 
 theme_bw() + xlab("Number of reds") + ylab("Probabilities")
```


# 3
## 3 (Q1)
```{r}
missing_proportion <-function(num_trial){
  set.seed(123)
  sampling_without_replacement_simulation <- data.frame(trial = 1:num_trial) %>%
    mutate(sample_balls = itermap(trial,
                                  function(x){
                                    sample(100, 10,replace=FALSE )
                                  })) %>%
    mutate(num_reds = itermap_dbl(sample_balls,
                                  function(x){sum(x<=50)}),
           num_blue = itermap_dbl(sample_balls,
                                  function(x){sum(x>50 & x<=80)}),
           num_green = itermap_dbl(sample_balls,
                                   function(x){sum(x>80 & x<=100)})) %>%
    mutate(min_count = pmin(num_reds, num_blue, num_green))
  
  missing_color_proportion <- mean(sampling_without_replacement_simulation$min_count == 0)
  return(missing_color_proportion)
}

num_trials <- c(10, 100, 500, 1000, 2000, 5000, 10000)
missing_proportion_data <- data.frame(num_trail = num_trials) %>%
  mutate(missing_proportion = itermap(num_trail,
                                       function(x){
                                         missing_proportion(x)
                                       }))
print(missing_proportion_data)

```

## 3 (Q2)
```{r}
number_missing1 <- choose(50,10)+choose(70,10)+choose(80,10)
number_missing2 <- choose(20,10)+choose(30,10)+choose(50,10)
number_all <- choose(100,10)
proportion_missing <- (number_missing1-number_missing2)/number_all
print(proportion_missing)
```