---
title: "Assignment02"
author: "zerofrom"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(Stat2Data)
```
# 1. Data Wrangling
```{r}
data("Hawks")
```

## 1.1 (Q1)   
Properties:
```{r}
names_variable <- colnames(Hawks)
print(names_variable)
```
Species names:
```{r}
data_species <- Hawks  %>%
  distinct(Species)
print(data_species)
```
Sample Weight data:
```{r}
weight_data <- Hawks  %>%
  distinct(Weight) 
head(weight_data,5)
```
#### Data Frame hSF:
```{r}
hSF <- Hawks %>%
  filter(Species == "RT", Weight >= 1000) %>%
  select(Wing, Weight, Tail)
head(hSF,5)
```


## 1.1 (Q2)   
#### How many variables does the data frame hSF have?
```{r}
num_variables <- ncol(hSF)
print(num_variables)
```
#### What would you say to communicate this information to a Machine Learning practitioner?
```{r}
answer <- paste("There are",num_variables,"variables in the data frame hSF used for training.")
print(answer)
```
#### How many examples does the data frame hSF have? How many observations? How many cases?
```{r}
num_examples <- nrow(hSF)
print(num_examples)
```

## 1.2 (Q1)
#### Sort by Wing:
```{r}
hSF_wing <- hSF %>%
  arrange(Wing)
head(hSF_wing,5)
```

## 1.3 (Q1)
#### hawkSpeciesNameCodes:
```{r}
hawkSpeciesNameCodes <- data.frame(
  species_code=c("CH","RT","SS"),
  species_name_full=c("Cooper's","Red-tailed","Sharp-shinned")
)
print(hawkSpeciesNameCodes)
```

## 1.3 (Q2)
#### hawksFullName:
```{r}
hawkFullName <- Hawks %>%
  left_join(hawkSpeciesNameCodes, by=c("Species"="species_code")) %>%
  select(-Species) %>%
  rename(Species=species_name_full) 
head(hawkFullName,7)
```

## 1.3 (Q3)
#### hawksFullName Select Print:
```{r}
hawkFullName_select <- hawkFullName %>%
  select(Species,Wing,Weight)
head(hawkFullName_select,7)
```

#### Does it matter what type of join function you use here? In what situations would it make a difference?
```{r}
print("A left_join B: Return all rows in A.")
print("A right_join B: Return all rows in B.")
print("A inner_join B: Return only the rows in both A and B based on the specified keys.")
print("A full_join B: Return all rows from both A and B")
```


## 1.4 (Q1)
#### bird BMI:
```{r}
hawksWithBMI <- Hawks %>%
  select(Species,Wing,Weight) %>%
  mutate(bird_BMI = 1000*Weight/(Wing*Wing)) %>%
  select(Species,bird_BMI) %>%
  arrange(desc(bird_BMI))
head(hawksWithBMI, 8)
```
....

## 1.5 (Q1)
#### Summarize_data:
```{r}
summary_data <- hawkFullName %>%
  filter(Wing != 0 | Tail != 0) %>% 
  group_by(Species) %>%
  summarize(
    num_rows = n(),
    mn_wing = mean(Wing, na.rm = TRUE),
    nd_wing = median(Wing, na.rm = TRUE),
    t_mn_wing = mean(Wing, trim=0.1, na.rm = TRUE),
    b_wt_ratio = max(Wing/Tail, na.rm = TRUE)
    ) %>%
  select(Species,num_rows,mn_wing,nd_wing,t_mn_wing,b_wt_ratio)
print(summary_data)
```

## 1.5 (Q2)
#### Summarize_na_number:
```{r}
summary_number <- hawkFullName %>%
  select(Species,everything()) %>%
  group_by(Species) %>%
  summarize(
    across(
      Wing:Tarsus,
      ~ sum(is.na(.))
    ),
    Crop = sum(is.na(Crop))
  )
print(summary_number)
```
....

# 2. Random experiments, events and sample spaces, and the set theory

....

# 3. Probability theory

## 3 (Q1)

## 3 (Q2)

.....
