---
title: "Assignment03"
author: "zerofrom"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(Stat2Data)
```
# 1. Data Wrangling
```{r}
data("Hawks")
```

## 1 (Q1) 
```{r}
hawksSmall<-
drop_na(select(Hawks,Age,Day,Month,Year,CaptureTime,Species,Wing,Weight
,Tail))
number<- dim(hawksSmall)
print(number)
head(hawksSmall,5)
```

## 1 (Q2) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Weight) 
) +
  geom_histogram(
    binwidth = 10
  ) +
  labs(
    x="Weight",
    y="Count"
   ) +
  theme_minimal()

```

## 1 (Q3) 
```{r}
# adjust = 0.5 
p1 <- ggplot(hawksSmall, aes(x=Tail)) +
  geom_density(adjust=0.5) +
  labs(
    x="Tail length",
    y="Count"
  )

# adjust = 2
p2 <- ggplot(hawksSmall, aes(x=Tail)) +
  geom_density(adjust=2) +
  labs(
    x="Tail length",
    y="Count"
  )
p1
p2
```

## 1 (Q4) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,color=Species)
  )+
  geom_density(
    adjust=1
    ) +
  labs(
    x="Tail length",
    y="Count"
  )
```

## 1 (Q5) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,y=Species,fill=Species)
)+
  geom_violin()+
  labs(
    x="Tail(mm)",
    y="Density"
  )
```

## 1 (Q6) 
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,y=Weight,color=Species,shape=Species)
)+
  geom_point()+
  labs(
    x="Tail(mm)",
    y="Weight(mm)"
  )
```  

1. There are 4 aesthetics: x=Tail,y=Weight,color=Species,shape=Species.  
2. Points.  
3. Color: Different colors refers to different species.  
   Shape: Different shapes refers to different species.  
   Axes Labels: These provide context for what the x(Tail length) and y(Weight) axes represent.  
   
## 1 (Q7)
```{r}
ggplot(
  hawksSmall,
  aes(x=Tail,y=Weight,color=Species)
)+
  geom_point()+
  geom_smooth(method = "lm")+
  facet_wrap(~Species,scales="free")+
  labs(
    x="Tail(mm)",
    y="Weight(mm)"
  )
```  

1. Color: Used to differentiate between species.  
   Line: A trend line indicates the relationship between Tail and Weight.  
3.The trend line shows a positive slope, which suggests positive correlation between the weight of the hawks and their tail lengths. 

## 1 (Q8)
```{r}
heaviest_hawk <-hawksSmall %>%
  filter(Weight == max(Weight)) %>%
  select(Tail, Weight)

ggplot(
  hawksSmall,
  aes(x=Tail,y=Weight,color=Species,shape=Species)
)+
  geom_point()+
  labs(
    x="Tail(mm)",
    y="Weight(mm)"
  )+
  geom_curve(
    aes(x=heaviest_hawk$Tail, y=heaviest_hawk$Weight-200,
        xend=heaviest_hawk$Tail, yend=heaviest_hawk$Weight),
    curvature = 0.5,
    arrow = arrow(length=unit(0.01,"inches"),
                  type="closed"),
    color="black"
  )+
  geom_point(
    aes(x=heaviest_hawk$Tail, y=heaviest_hawk$Weight),
    shape=16,
    size=1,
    color="black"
  )+
  annotate("text",
           x=heaviest_hawk$Tail,
           y=heaviest_hawk$Weight -200,
           label="heaviest hawk")
```