---
title: "Assignment02"
author: "zerofrom"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(Stat2Data)
```
# 1. Data Wrangling
```{r}
data("Hawks")
```

## 1.1 (Q1)   
Properties:
```{r}
names_variable <- colnames(Hawks)
print(names_variable)
```
Species names:
```{r}
data_species <- Hawks  %>%
  distinct(Species)
print(data_species)
```
Sample Weight data:
```{r}
weight_data <- Hawks  %>%
  distinct(Weight) 
head(weight_data,5)
```
#### Data Frame hSF:
```{r}
hSF <- Hawks %>%
  filter(Species == "RT", Weight >= 1000) %>%
  select(Wing, Weight, Tail)
head(hSF,5)
```


## 1.1 (Q2)   
#### How many variables does the data frame hSF have?
```{r}
num_variables <- ncol(hSF)
print(num_variables)
```
#### What would you say to communicate this information to a Machine Learning practitioner?
```{r}
answer <- paste("There are",num_variables,"variables in the data frame hSF used for training.")
print(answer)
```
#### How many examples does the data frame hSF have? How many observations? How many cases?
```{r}
num_examples <- nrow(hSF)
print(num_examples)
```

## 1.2 (Q1)
#### Sort by Wing:
```{r}
hSF_wing <- hSF %>%
  arrange(Wing)
head(hSF_wing,5)
```

## 1.3 (Q1)
#### hawkSpeciesNameCodes:
```{r}
hawkSpeciesNameCodes <- data.frame(
  species_code=c("CH","RT","SS"),
  species_name_full=c("Cooper's","Red-tailed","Sharp-shinned")
)
print(hawkSpeciesNameCodes)
```

## 1.3 (Q2)
#### hawksFullName:
```{r}
hawkFullName <- Hawks %>%
  left_join(hawkSpeciesNameCodes, by=c("Species"="species_code")) %>%
  select(-Species) %>%
  rename(Species=species_name_full) 
head(hawkFullName,7)
```

## 1.3 (Q3)
#### hawksFullName Select Print:
```{r}
hawkFullName_select <- hawkFullName %>%
  select(Species,Wing,Weight)
head(hawkFullName_select,7)
```

#### Does it matter what type of join function you use here? In what situations would it make a difference?
```{r}
print("A left_join B: Return all rows in A.")
print("A right_join B: Return all rows in B.")
print("A inner_join B: Return only the rows in both A and B based on the specified keys.")
print("A full_join B: Return all rows from both A and B")
```


## 1.4 (Q1)
#### bird BMI:
```{r}
hawksWithBMI <- Hawks %>%
  select(Species,Wing,Weight) %>%
  mutate(bird_BMI = 1000*Weight/(Wing*Wing)) %>%
  select(Species,bird_BMI) %>%
  arrange(desc(bird_BMI))
head(hawksWithBMI, 8)
```
....

## 1.5 (Q1)
#### Summarize_data:
```{r}
summary_data <- hawkFullName %>%
  filter(Wing != 0 | Tail != 0) %>% 
  group_by(Species) %>%
  summarize(
    num_rows = n(),
    mn_wing = mean(Wing, na.rm = TRUE),
    nd_wing = median(Wing, na.rm = TRUE),
    t_mn_wing = mean(Wing, trim=0.1, na.rm = TRUE),
    b_wt_ratio = max(Wing/Tail, na.rm = TRUE)
    ) %>%
  select(Species,num_rows,mn_wing,nd_wing,t_mn_wing,b_wt_ratio)
print(summary_data)
```

## 1.5 (Q2)
#### Summarize_na_number:
```{r}
summary_number <- hawkFullName %>%
  select(Species,everything()) %>%
  group_by(Species) %>%
  summarize(
    across(
      Wing:Tarsus,
      ~ sum(is.na(.))
    ),
    Crop = sum(is.na(Crop))
  )
print(summary_number)
```
....

# 2. Random experiments, events and sample spaces, and the set theory
## 2.1 (Q1)
**Random experiments: ** A random experiment is a procedure that meet both of the following conditions:

(1) has a well-defined set of possible outcomes;

(2) could (at least in principle) be repeated arbitrarily many times.


**Events: ** An event is a set of possible outcomes of an experiment.

**Sample spaces: ** A sample space is the set of possible outcomes of interest for a random experiment.

**The set theory: ** A set is just a collection of objects of interest, such as the possible outcomes.

## 2.1 (Q2)

**Example: ** The result of both rolls of the dice is the same: {(1,1),(2,2),(3,3),(4,4),(5,5),(6,6)}

**Sample space: **{

(1,1),(1,2),(1,3),(1,4),(1,5),(1,6),

(2,1),(2,2),(2,3),(2,4),(2,5),(2,6),

......
(6,1),(6,2),(6,3),(6,4),(6,5),(6,6)}

**Total number: ** 2^36

**Is the empty set considered as an event: ** Yes, it represents the event where no outcome occurs, meaning an impossible event.

## 2.2 (Q1)
A ∪ B = {1, 2, 3, 4, 6}  
A ∪ C = {1, 2, 3, 4, 5, 6}  
A ∩ B = {2}  
A ∩ C = ∅   
A ∖ B = {1, 3}   
A ∖ C = {1, 2, 3}   
A and B are not disjoint  
A and C are disjoint  
B and A ∖ B are disjoint  
Partition into two sets: {{1, 3, 5}, {2, 4, 6}}  
Partition into three sets: {{1, 6}, {2, 3}, {4, 5}}  

## 2.2 (Q1)
1.
$$(A^c)^c = A$$  
2. 
$$\Omega^c = \emptyset$$  
3. 
Let $x \in B^c$, then $x \notin B$.  
Since $A \subseteq B$，then $x \notin A$，so $x \in A^c$.  
Therefore，$B^c \subseteq A^c$.  
4.
\[
(A \cap B)^c = \{ x \in \Omega : x \notin A \cap B \}
\]  
It means that  \( x \) is either not in \( A \) or not in \( B \).   
Therefore,  
\[
(A \cap B)^c = A^c \cup B^c
\]  
Let’s suppose a sequence of events \( A_1, A_2, \dots, A_K \subseteq \Omega \).  
The general form of this law for the intersection of multiple sets is:
\[
\left( \bigcap_{k=1}^{K} A_k \right)^c = \bigcup_{k=1}^{K} A_k^c
\]  
5. 
 The complement of the union \( A \cup B \) is the set of all elements not in \( A \cup B \):
\[
(A \cup B)^c = \{ x \in \Omega : x \notin A \cup B \}
\]
This means that \( x \) is neither in \( A \) nor in \( B \).  
This means that 
\[
x \in A^c \quad \text{and} \quad x \in B^c
\]
This means that 
\[
x \in A^c \cap B^c
\]
Therefore  
\[
(A \cup B)^c = A^c \cap B^c
\]

6.
the complement of the union of multiple sets is the intersection of their complements:
\[
\left( \bigcup_{k=1}^{K} A_k \right)^c = \bigcap_{k=1}^{K} A_k^c
\]
This is a generalization of the law for multiple events.  

## 2.2 (Q3)
For each element \( w_i \in \Omega \), when forming a subset \( A \), we have two choices:  
1. Include the element \( w_i \).  
2. Exclude the element \( w_i \).  

This means that for every element, there are two possible outcomes.  
Since there are \( K \) elements in \( \Omega \), the total number of subsets can be calculated as follows:
\[
|E| = 2^K
\]

## 2.2 (Q4)
1.  
the empty set \( A = \emptyset \) is a valid choice. The intersection of the empty set with any other set is empty, so it is disjoint from all other sets.
2.  

....  

# 3. Probability theory

## 3 (Q1)

## 3 (Q2)

.....
